Deriving Multi-Headed Projective Dependency Parses \\ from Link Grammar Parses

### 2014-06-03 doc/LinksToDAG.tex
back to 4 pp
FINAL SUBMISSION - BUT WARNING - THE APPENDICES USE TOO SMALL A RUN AND THE GRAPH IS OUT OF DATE AS WELL - TRY TO RESUBMIT BY EMAIL Edited and clarified business about subject-verb direction Munged table for Appendix A to use longtable Removed triple pdflatex call in makefil

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took 1.5 hours. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, only \input{figure/allowed_labels_both.tex}of \input{figure/allowed_labels_total.tex}link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = \input{figure/label_token_disallowed}$ of \input{figure/label_token_total}link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences but only 0.15\% of the Russian sentences had at least one multiheaded word.
\noteJE{2 significant digits is enough}
\noteJE{update these numbers}

@@

The main vexation is that subject-verb links are handled inconsistently.  Under the English link grammar, the verb (or 0) that governs a clause will link to both the clause's subject and its last (main) verb.  This ought to give us the desired treatment of {\em ``Jill persuaded him to skip''}, in which {\em ``him''} has two parents.  Unfortunately, it does not, because of inconsistencies in the link grammar itself.\footnote{When the subject is missing ({\em ``Jill wanted to skip''}), the governing verb now links instead to the clause's first (tensed) verb but {\em no longer} to the last as well.  That favors a consistent solution where each auxiliary verb is a parent of the verb to its right ({\em to} $\rightarrow$ {\em skip}).  As a result, when the subject is present, it must be the {\em parent} of the first verb, which otherwise would not have a parent ({\em him} $\rightarrow$ {\em to} $\rightarrow$ {\em skip}).  Yet also, subjects must be {\em children} of verbs in a few  inconsistently handled constructions such as non-embedded reported speech ({\em ``It was impossible, they said''}), since the subject ({\em ``they''}) links only to the verb ({\em ``said''}) and so has no other possible parent.}

>>>>

We solved our ILP problem using the SCIP Optimization Suite \cite{achterberg2009scip}, encoding it using the ZIMPL language \cite{Koch2004}.  Our largest run took 1.5 hours. \noteJH{A run of 10,000 sentences takes 3142 seconds (update in final version!)}  Detailed results from this run are included as Appendix~\ref{app:linktypes}.  On English, only \input{figure/allowed_labels_both.tex}of \input{figure/allowed_labels_total.tex}link {\em types} allowed both directions, and only $\sum_{ij} s_{ij} = \input{figure/label_token_disallowed}$ of \input{figure/label_token_total}link {\em tokens} required a disallowed direction via slack.
\input{figure/conll_analysis_sentences_multiheaded}of the English sentences but only 0.15\% of the Russian ones had at least one multiheaded word.
\noteJE{2 significant digits is enough}
\noteJE{update these numbers}

@@

The main vexation is the handling of subject-verb links.  Under the English link grammar, the verb (or 0) that governs a clause will link to both the clause's subject and its last (main) verb.  This ought to give us the desired treatment of {\em ``Jill persuaded him to skip''}, in which {\em ``him''} has two parents.  Unfortunately, we get {\em him} $\rightarrow$ {\em to}, because of inconsistencies in the link grammar itself.\footnote{When the subject is missing ({\em ``Jill wanted to skip''}), the governing verb now links instead to the clause's first (tensed) verb but {\em no longer} to the last as well.  That favors a consistent solution where each auxiliary verb is a parent of the verb to its right ({\em to} $\rightarrow$ {\em skip}).  As a result, when the subject is present, it must be the {\em parent} of the first verb, which otherwise would not have a parent ({\em him} $\rightarrow$ {\em to} $\rightarrow$ {\em skip}).  (Yet subjects are not {\em always} parents.  The occasional construction {\em ``It was impossible, they said''} is handled inconsistently by the link grammar:
the subject ({\em ``they''}) links only to the verb ({\em ``said''}) and so must be its child, no other parent being available.)}
